### 2015-02-16 paper_40_mpi.tex
working on SQL
working to add some survey info

        \subsubsection{SATISFACTION}
            The satisfaction of users, customers, and/or business partners is 
            the third element to be measured.  This element is important because 
            in an established business, retaining customers is less expensive
            than actracting new customers \cite{Aulet2013}.  
            Depending upon the type of SDO,
            the customers may be internal or external to the organization.
            If one element of MPI was to be rated as the most important, satisfaction
            would be it.  Without satisfied customers, the rest of the measures do not matter.
            For example, having a quality
            application that is always available does not matter if it is not what the customer
            wants.  Surveys are used to measure satisfaction for MPI.

            \paragraph{SURVEYS}
                Write possible survey questions here.
                and explain the issues with surveys, see qualifier

@@

                    Application ID & String  & Required \\
                    \myrowcolour%
                    Frequency Date & Date & Required \\
                    Scheduled Start Date & Date & Required \\
                    \myrowcolour%
                    Scheduled Finish Date & Date & Required \\
                    Actual Start Date & Date  & Required \\
                    \myrowcolour%
                    Actual Finish Date & Date  & Required \\

>>>>

        \subsubsection{SATISFACTION}
            The satisfaction of users, customers, and/or business partners is 
            the third element to be measured.  This element is important because 
            in an established business, retaining customers is less expensive
            than attracting new customers \cite{Aulet2013}.  
            Depending upon the type of SDO,
            the customers may be internal or external to the organization.  For
            the remainder of this section, the term customer will be used
            to represent any person who is responsible for guidance, decision-making
            or use of the software.  The term customer can refer to a: user, paying or nonpaying
            customer, internal or external business partner, or any other person deemed influential
            to the development of the software.

            \textit{If one element of MPI was to be rated as the most important, satisfaction
            would be it.}  
            Without satisfied customers, the rest of the measures do not matter.
            For example, having a quality
            application that is always available does not matter if the
            application is not what the customer wants.

            Surveys are used to measure satisfaction for MPI.  A series of questions will
            be presented to all or a subset of the customers.  Any customer that chooses
            to respond to the survey is considered a respondent.  A respondent can rate
            questions with a numerical response where the minimum value indicates maximum
            disagreement and the maximum value indicates
            the maximum agreement. Common rating scales would be
            from 1 to 5 or from 1 to 3.  An example survey can be seen in Table 
            \ref{tab:samplesurvey}.

            \begin{longtable}{@{}l rr rr}
                \toprule%
                 \centering%
                 {\bfseries ID}
                 & {\bfseries Question}
                 & {\bfseries Disagree}
                 & {\bfseries Neutral}
                 & {\bfseries Agree}  \\

                \cmidrule[0.4pt](r{0.125em}){1-1}%
                \cmidrule[0.4pt](lr{0.125em}){2-2}%
                \cmidrule[0.4pt](l{0.125em}){3-3}%
                \cmidrule[0.4pt](l{0.125em}){4-4}%
                \cmidrule[0.4pt](l{0.125em}){5-5}%
                % \midrule
                \endhead

                1 & I find the software easy to use.  & & & \\
                \myrowcolour%
                2 & I would recommend this software to others. & & & \\
                3 & The software makes me more productive. & & & \\
                \myrowcolour%
                4 & I am happy with this software. & & & \\

                \caption{SAMPLE SURVEY FOR SATISFACTION}
                \label{tab:samplesurvey}
            \end{longtable}

            \paragraph{ISSUES WITH SURVEYS}

                There are 2 cases of surveys that could be used for satisfaction.  First is when an SDO is part of a larger organization.  Typically there are a small number of business partners that help to guide and direct the work performed by the SDO.  In this case, the business partners are the ones offering survey responses and they should all be willing to respond.  Thus, those business partners represent the entire population, and the surveys should result in a 100\% response rate which is technically a census.  
         The only bias that will be present here is the bias of the business partners and sampling cannot control for that.

       In the other case, end-users will be surveyed for satisfaction. Obviously, the entire population cannot be surveyed, so a probability sample should be randomly created. Even then, bias will be present.  First, not all users will respond.  This is because survey respondents tend to sit at the extremes of either satisfied or dissatisfied.  Thus the results will tend to indicate that separation. Second, even with probability  sampling it is possible to miss entire groups of population members. For example consider a banking application such as a savings account, a survey would most likely be presented online and it would have a coverage bias due the exclusion of savings account holders that do not bank online.  Third, a selection bias can occur when some members of the population have a higher probability of inclusion in the sampling frame than others.  One example could be a user with multiple savings accounts.  The selection bias is typically easy to avoid if the bias is identified.  Weighting is a common solution here.

@@

                    Application ID & String  & Required \\
                    \myrowcolour%
                    Frequency Date & Date & Required \\
                    Scheduled Start Date & Date & Required \\
                    \myrowcolour%
                    Scheduled Finish Date & Date & Required \\
                    Actual Start Date & Date  & Optional \\
                    \myrowcolour%
                    Actual Finish Date & Date  & Required \\

### 2015-02-16 paper_80_conclusion.tex
capitalize titles and rearrange  sections
working to add some survey info

% new section
\section{Conclusions}

>>>>

\section{FUTURE WORK}

Due to the number of issues with surveys.  One area of future work would be indentifying
a general set of questions that would best fit MPI.  This set would have to include
the best number of questions, order of questions and wording of questions.  Therefore,
any new organization would not have to determine their own survey, but rather just use the
predetermined set of questions.  It would even be advantageous to build a software system to
handle the survey distribution and collection.  Ideally, the results would automatically be
inserted into the appropriate database tables for MPI scoring.

% new section
\section{CONCLUSION}
